Implications of afforestation policies for global markets

### 2023-06-01 paper.Rmd
Update paper.Rmd

This project contributes to the literature by melding together two widely accepted global models, the Global Trade Analysis Project (GTAP) computable general equilibrium model and the Global Timber Model (GTM), to better assess the outcomes of several likely scenarios.

>>>>

This project will assess the impact of various likely scenarios by melding together two widely accepted global models, the Global Trade Analysis Project (GTAP) computable general equilibrium model [@aguilar2022] and the Global Timber Model (GTM) [@sohngen2001]. The GTAP model has traditionally been used to analyze the impact of various shocks on things like agricultural prices and trade volumes. However, the standard model does not well account for land-use changes, and the GTAP Land Use and Land Cover (LULC) database has limitations due to its infrequent updates. The GTM is quite helpful in getting around these issues, as it is a dynamic optimization model that can examine the impact of afforestation or avoided deforestation on the carbon sink. By joining the two models and passing outputs back and forth between the models, any limitations of either model can be minimized and more robust results, therefore, can be attained.
